Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2022-05-05 FDT2020/Introduction.tex
typo fix

\subsubsection{2-edge-connected multi-subgraph problem}
\label{sec:2EC-intro}
Known polyhedral structure makes it easier to study integrality gaps for such problems. In particular, for the subtour-elimination relaxation \cite{carrravi,boydcarr,Carr2004} introduced fundamental extreme points that create the ``hardest'' LP solutions to decompose.

>>>>

\subsubsection{2-edge-connected multi-subgraph problem}
\label{sec:2EC-intro}
Known polyhedral structure makes it easier to study integrality gaps for such problems. In particular, for the subtour-elimination relaxation, \cite{carrravi,boydcarr,Carr2004} introduced fundamental extreme points that create the ``hardest'' LP solutions to decompose.
